func-descr.template

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd

Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) parameter) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row. This is true for each row except the first, for which the value is always zero.

@@

@@

#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) Function {#func.RMSE_kable}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
It is assumed that the table has the following three columns:

@@

::: { #func.RMSE_kableusage .sidebar }
##### Usage
\

```{r eval=FALSE}
RMSE_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 5,
                       col3width = 30)
```
:::

@@

::: { #func.RMSE_kable.args.col1width .sidebar }
  - ***col1width:*** Width of the first column;

@@

::: { #func.RMSE_kable.args.col2width .sidebar }
  - ***col2width:*** Width of the second column;

@@

::: { #func.RMSE_kable.args.col3width .sidebar }
  - ***col3width:*** Width of the third column;

@@

::: { #func.RMSE_kablecode .sidebar }
##### Source Code
\

The soure code of the function is provided below:
```{r eval=FALSE}
RMSE_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 5,
                       col3width = 30){
  RMSEs |>
    kable(align='lcl', booktabs = T, padding = 5) |> 
    row_spec(0, bold = T) |>
    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
}
```
:::

#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) Function {#func.RMSE.Total_kable}
\

::: {.noteblock data-latex=""}
The complete source code of this function is available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L32) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L85) script on _GitHub_.
:::

::: {.noteblock data-latex=""}
It is assumed that the table has the following four columns:

@@

```{r eval=FALSE}
RMSE.Total_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 7,
                       col3width = 5,
                       col4width = 25)
```
:::

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** _RMSEs Result Tibble_ to print;

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col1width:*** Width of the first column;

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col2width:*** Width of the second column;

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col3width:*** Width of the third column;

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col4width:*** Width of the fourth column;

::: { #func.RMSE.Total_kablecode .sidebar }
##### Source Code
\

The soure code of the function is provided below:
```{r eval=FALSE}
RMSE.Total_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 7,
                       col3width = 5, 
                       col4width = 25){
  RMSEs |> 
    RMSE_kable(col1width,
               col2width,
               col3width) |>
    column_spec(column = 4, 
                width = RSME.tibble.col_width(col4width)) 
}

::: {.noteblock data-latex=""}
Under the hood, the function calls internally the [RMSE_kable](#func.RMSE_kable) function described above.
:::
:::

>>>>

Adds a calculated column named _Diff_ to the _RMSEs Result Tibble_ (passed in the [RMSEs](#func.RMSEs.AddDiffColumn.args.RMSEs) argument) that contains, for each row, the difference between the value of the _RMSE_ column for the previous row and the value of the same column for the current row. This is true for each row except the first, for which the value is always zero.

@@

For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
:::

@@

#### [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) Function {#func.RSME.tibble.col_width}
\

Converts the _RMSEs Result Tibble_ column width value passed in argument [x](#func.RSME.tibble.col_width.args.x) to a character string compatible for use as the `width` argument value to pass to the [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function.

::: { #func.RSME.tibble.col_width.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
width_em <- RSME.tibble.col_width(x)
```
:::

::: { #func.RSME.tibble.col_width.args .sidebar }
##### Arguments
\

::: { #func.RSME.tibble.col_width.args.x .sidebar }
  - ***x:*** (Numeric) Column width value to be formatted;

::: { #func.RSME.tibble.col_width.details .sidebar }
##### Details
\

This is a utility function, a wrapper for the [msg.glue](#func.msg.glue) function described above, which is called internally to format the value passed in argument [x](#func.RSME.tibble.col_width.args.x) for subsequent passing to the function [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) as a value of the `width` argument.
:::

::: { #func.RSME.tibble.col_width.value .sidebar }
##### Value
\

A character string representing the formatted column width value.
:::

::: { #func.RSME.tibble.col_width.code .sidebar }
##### Source Code
\

The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is shown below:
```{r eval=FALSE}
RSME.tibble.col_width <- function(x){
  "%1em" |> msg.glue(x)
}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RSME.tibble.col_width](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L66) script on _GitHub_.
:::

#### [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) Function {#func.RMSE_kable}
\

@@

::: {.noteblock data-latex=""}
It is assumed that the tibble has the following three columns:

@@

::: { #func.RMSE_kable.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
RMSE_kable(RMSEs,
           col1width = 15,
           col2width = 5,
           col3width = 30)
```
:::

@@

::: { #func.RMSE_kable.args.col1width .sidebar }
  - ***col1width:*** Width of the first column (15 by default);

@@

::: { #func.RMSE_kable.args.col2width .sidebar }
  - ***col2width:*** Width of the second column (5 by default);

@@

::: { #func.RMSE_kable.args.col3width .sidebar }
  - ***col3width:*** Width of the third column (30 by default).

::: { #func.RMSE_kable.details .sidebar }
##### Details
\

This function is a wrapper for the [knitr::kable](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable) function, which is called internally to create a table (based on the _RMSEs Result Tibble_ data), formatted for output in the project report.

The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to specify the width of the table columns.

For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
:::

::: { #func.RMSE_kable.value .sidebar }
##### Value
\

The table created by the internally called [knitr::kable()]().

@@

::: { #func.RMSE_kable.code .sidebar }
##### Source Code
\

The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is shown below:
```{r eval=FALSE}
RMSE_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 5,
                       col3width = 30){
  RMSEs |>
    kable(align='lcl', booktabs = T, padding = 5) |> 
    row_spec(0, bold = T) |>
    column_spec(column = 1, width = RSME.tibble.col_width(col1width)) |>
    column_spec(column = 2, width = RSME.tibble.col_width(col2width)) |>
    column_spec(column = 3, width = RSME.tibble.col_width(col3width)) 
}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSE_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L43) script on _GitHub_.
:::

#### [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) Function {#func.RMSE.Total_kable}
\

Prints the final _RMSEs Result Tibble_.

::: {.noteblock data-latex=""}
It is assumed that the tibble has the following four columns:

@@

```{r eval=FALSE}
RMSE.Total_kable(RMSEs,
                 col1width = 15,
                 col2width = 7,
                 col3width = 5,
                 col4width = 25)
```
:::

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** The final _RMSEs Result Tibble_ to print;

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col1width:*** Width of the first column (15 by default);

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col2width:*** Width of the second column (7 by default);

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col3width:*** Width of the third column(5 by default);

@@

::: { #func.RMSE.Total_kable.args. .sidebar }
  - ***col4width:*** Width of the fourth column (25 by default);

::: { #func.RMSE.Total_kable.details .sidebar }
##### Details
\

This function is a wrapper for the [RMSE_kable](#func.RMSE_kable) function described above, which is called internally to print the table, created from the final _RMSEs Result Tibble_ data.

The [kableExtra::column_spec](https://www.rdocumentation.org/packages/kableExtra/versions/1.3.4/topics/column_spec) function, along with the [RSME.tibble.col_width](#func.RSME.tibble.col_width) function described above, are also used internally to set the width of the last column of the table.

For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
:::

::: { #func.RMSE.Total_kable.value .sidebar }
##### Value
\

The table returned by the internally called [RMSE_kable()](#func.RMSE_kable).
:::

::: { #func.RMSE.Total_kable.code .sidebar }
##### Source Code
\

The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is shown below:
```{r eval=FALSE}
RMSE.Total_kable <- function(RMSEs,
                       col1width = 15,
                       col2width = 7,
                       col3width = 5, 
                       col4width = 25){
  RMSEs |> 
    RMSE.Total_kable(col1width,
               col2width,
               col3width) |>
    column_spec(column = 4, 
                width = RSME.tibble.col_width(col4width)) 
}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSE.Total_kable](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L54) script on _GitHub_.
:::

### 2025-11-02 reports/capstone-movielens.site/work/func-descr.template.Rmd

>>>>

#### [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.tibble_tmpl}
\

Modifies the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.tibble_tmpl.args.RMSEs) argument.

::: { #func.RMSEs.tibble_tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
```
:::

::: { #func.RMSEs.tibble_tmpl.args .sidebar }
##### Arguments
\

::: { #func.RMSEs.tibble_tmpl.args.RMSEs .sidebar }
  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

::: { #func.RMSEs.tibble_tmpl.details .sidebar }
##### Details
\

This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
:::

::: { #func.RMSEs.tibble_tmpl.value .sidebar }
##### Value
\

The modified tibble returned by the internally called [tibble::()]().

::: { #func.RMSEs.tibble_tmpl.code .sidebar }
##### Source Code
\

The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::

\newpage
